\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-11-10 manuscript.Rnw
Add figure for 4-state disease progression model

>>>>

\begin{figure}[h]
\centering
\begin{tikzpicture}
% States
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S1) {\textbf{State 1}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S2) [right = of S1] {\textbf{State 2}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (S3) [right = of S2] {\textbf{State 3}};
\node[draw, minimum height=1cm, minimum width=2cm, font=\footnotesize] (D) [below = of S2] {\textbf{Death}};

% Arrows
\draw [thick, <->] (S1.east) -- (S2.west);
\draw [thick, ->] (S2.east) -- (S3.west);
\draw [thick, ->] (S1.south) -- (D.west);
\draw [thick, ->] (S2.south) -- (D.north);
\draw [thick, ->] (S3.south) -- (D.east);

\end{tikzpicture}
\caption{Four state disease progression model}\label{fig:econ-eval-process-hesim}
\end{figure}
